Gravitational Lens Recovery with \Glass: How to measure the mass profile and shape of a lens

### 2013-09-06 limits/ms.tex
more action items

>>>>

\item Change variable chi to something else ($f$?) to avoid confusion
  with $\chi^2$.

\item Replace equation 20 with what you are actually doing when
  calculating $chi$ (now $f$).

\item Add plot of $chi$ ($f$) for $lambda_1/lambda_2$ and theta shape
  parameters (c.f. what Claudio is doing).

\item Check that you and Claudio average to the same projected radius
  (one pixel past outermost image) when calculating
  $lambda_1/lambda_2$ and $\theta$.

\item Calculate aperture averaged $\sigma$ to 2 (or 3 you decide) half
  light radii assuming $beta = 0$ for a model (double) where the mass
  is poorly constrained by strong lensing. Accept/reject models from
  the ensemble $\Longrightarrow$ what we learn from combined lensing
  kinematics.

\item Take a model that is well constrained by strong lensing
  (e.g. quad with time delays). Calculate $\sigma_p(R)$ for each model
  in the ensemble using the kinematics module. Compare this with the
  true $\sigma_p(R)$ from the mock data to obtain a $\chi^2$ (actually
  a $\chi^2$ this time!).  Show the true $\sigma_p(R)$ and overlay
  coloured bands from the lensing model ensemble assuming $\beta = 0$
  or $\beta = 1$.
